%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Copyright 2015 Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Alessandro }{Candolini}
%\address{via Monte Grappa 44, 33100, Udine, Italy}
\address{London, UK}
%\mobile{(+39) 333-43-87-420}
\mobile{+44 7402 554023}
%\mobile{00447402554023}
%%% Social
\email{alessandro.candolini@gmail.com}
\skype{alessandro.candolini}
%\homepage{www.posquit0.com}
\github{acando86} 
\linkedin{alessandrocandolini}  
%%% Optionals
\position{Physicist 
{\enskip\cdotp\enskip} Software Developer
}
%\quote{``Make the change that you want to see in the world."}

%I am looking for positions sitting at the crossroad between modern 
%algorithms, new technology and the computational challenges of
%writing code which is beautiful, efficient and reliable.  
\quote{
I am an Italian theoretical physicist with heavy mathematical 
background, problem-solving attitude, and genuine passion for statistical data
analysis, software engineering, 
and modern technology. My current interests range from pure functional
programming to data science. 
Although I'm flexible enough to fit the problem at hand and confidently 
deliver 
fast solutions to  
highest priority tasks if 
required, 
I am a precise person and I prefer to do things the way they
should be done whenever possible. 
Currently I'm working as Android developer and this allows me to master 
mobile technologies, an important ingredient of the software 
development landscape.  
At the same time, I enjoy  working in a dynamic
environment where I have chances not only to improve my knowledge of the Android
 ecosystem and the software development process in general, but 
 also where I can  keep an eye on (and borrow ideas and technology from) emerging trends and metodologies in related
fields. 
 I firmly
believe in the future of highly cross-disciplinary fields.
I am looking for a position sitting at the crossroad between modern
algorithms, new technologies 
and the computational challenges of writing code which is clean, efficient
and reliable.
My ideal job would involve working in a stimulating, innovative team where I
can give valuable insights that help the company to grow  and at the same time
where I have the opportunity to improve myself and my skills.
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV using personal data
\makecvfooter

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Import contents
\import{\sectiondir}{my_skills.tex}
\import{\sectiondir}{jobs.tex}
\import{\sectiondir}{my_education.tex}
\import{\sectiondir}{my_extracurricular.tex}
\import{\sectiondir}{scholarships.tex}
\import{\sectiondir}{pubblications.tex}
\import{\sectiondir}{hobbies.tex}
%\import{\sectiondir}{presentation.tex}
%\import{\sectiondir}{writing.tex}
%\import{\sectiondir}{committees.tex}

\end{document}
