\cvsection{About me}

\begin{cvparagraph}
Theoretical physicist with heavy mathematical and statistical 
background, smart at problem-solving, skilled and truly passionate in software engineering, with almost 10 years of professional experience in industry. Goal-oriented and delivery-focused, I see technology as an enabler for business and I am always looking for optimal tradeoffs between engineering and business.

  For the past several years, I have been working as technical lead and senior Scala software engineer in cross-functional product teams, designing and implementing several business-critical backend systems in response to user and product needs, fostering  across the organisation a genuine culture of pragmatism, incremental development, accountability, ownership, and leveraging my strong engineering skills 
 % design principles, functional programming, CI/CD practices, telemetry, TDD and more 
  to develop production-grade systems at scale. Fast feedback loop is not just a good practice for me: it has always been part of my lifestyle.

  My current interests range from strongly statically typed purely functional programming, to concurrency and distributed systems, to learn formal specification tools like TLA+, to Bayesian inference. These (and others) are powerful weapons in my toolkit to confidently deliver robust, reliable, correct, flexible, high quality software and impactful results at pace. 

My background as a physicist, my diversified experiences and my strategic thinking make me a valuable asset to approach challenging and ambitious tasks. I'm looking for adventures where I can solve real problems and where I can grow and learn new things while helping the business and the team to successfully achieve their goals. 
\end{cvparagraph}
