
\cvsection{Continuing Education}


\cvsubsection{MOOCs}
\begin{cvhonors}
  \cvhonor
{Machine Learning}
{Statement of Accomplishment of Andrew Ng's Machine Learning course. 
   Website:
   \url{https://www.coursera.org/learn/machine-learning/home/info}}
{Coursera}
{2014}

\end{cvhonors}


\cvsubsection{Workshop and schools in Physics}

\begin{cvhonors}
  \cvhonor
{Conference on Long-Range-Interacting Many Body Systems: from Atomic to
   Astrophysical Scales }
{Attended in streaming.  Website: \url{http://indico.ictp.it/event/7612/}}
{ICTP, Trieste (Italy)}
{2016}

  \cvhonor
{Spring School on Superstring Theory and Related Topics}
{Attended in streaming (due to work).  Website: \url{http://indico.ictp.it/event/7624/}}
{ICTP, Trieste (Italy)}
{2016}


  \cvhonor
{School on Supersymmetry and Unification of Fundamental Interactions (Pre-SUSY 2013)}
{%Attended the school as partecipant at 
   Attented as partecipant. 
   %International Center for Theoretical Physics (ICTP). 
   Website: 
   \url{http://presusy2013.ictp.it/}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{ICTP, Trieste (Italy)}
%{20 August 2013 - 23 August 2013}
{2013}

  \cvhonor
{Workshop on Ultracold Atoms \& Gauge Theories}
{%Attended the workshop as partecipant at International Center for Theoretical
  % Physics (ICTP).  Webpage of the workshop:
   Attented as partecipant. 
   %International Center for Theoretical Physics (ICTP). 
   Website:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?ida=a12184}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{ICTP, Trieste (Italy)}
%{13 May 2013 - 17 May 2013}
{2013}

  \cvhonor
{Workshop on Majorana Fermions, Non-Abelian Statistics and Topological Quantum Information Processing}%
{%Attended the workshop as partecipant at 
   Attented as partecipant. 
   %International Center for Theoretical
%   Physics (ICTP). 
   %Webpage of the workshop:
   Website:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?email=0&ida=a11183}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{ICTP, Trieste (Italy)}
%{20 August 2012 -- 24 August 2012}
{2012}

  \cvhonor
{Ph.D. Course of Introduction to Bayesian methods}
{I attended \emph{as volounteer} the Ph.D. course of Introduction to Bayesian methods (Prof.
   E.~Milotti).
Topics covered: Bayesian inference, Maximum-Entropy and its applications
to image restoration, EM algorithm, Markov-Chain Monte Carlo, Hidden Markov
models, 
naive Bayesian learning and 
Bayesian classifiers (AUTOCLASS). 
Website:
\url{http://wwwusers.ts.infn.it/~milotti/Didattica/Bayes/Bayes.html}
}
{Trieste (Italy)}
{2010}%





 \end{cvhonors}









