\cvsection{About me}

\begin{cvparagraph}
I am an Italian theoretical physicist with heavy mathematical and statistical 
background, smart at problem-solving, and truly passionate about software engineering. 
Although  
confident in
delivering 
fast solutions at pace
if/when
business-critical, I love quality. 
In the last years I have been working primarily as Android software engineer,  
	making informed and effective usage of design principles, clean code, architecture and TDD to drive the development of production-ready apps.
These are my weapons of choice to safely approch either new features as well as to mitigate the risks involved whenever dealing with unavoidable legacy code, and I devote my effort to spread these techniques across my teammates. 
I'm always looking for the the best tradeoff between engineering and business needs. 
I enjoy  working in a dynamic
environment 
 where I can also keep an eye on (and borrow ideas, patterns, and technology from) emerging trends in related
	fields (eg, backend).
	My current interests include functional programming, category theory, concurrency and machine learning. 
 I firmly
believe in the future of highly cross-disciplinary fields.
My background as a physicist and my diversified work experiences make me a valueable asset to approach challenging tasks. 
My ideal job would involve working in a stimulating team where I feel an appreciation for quality, when 
can play a key role helping the company to grow their business and at the same time
where I have the opportunity to improve myself and my skills.
\end{cvparagraph}
