\cvsection{Extracurricular Activity}
\begin{cventries}
\cventry
{Machine Learning}
{Coursera}
{}
{December 17, 2014}
{Statement of Accomplishment of Machine Learning course by Professor Andrew Ng
   from Standford University.
   Website of the course:
   \url{https://www.coursera.org/learn/machine-learning/home/info}}


\cventry
{School on Supersymmetry and Unification of Fundamental Interactions (Pre-SUSY
   2013)}
   {International Center for Theoretical Physics (ICTP)}
{Trieste (Italy)}
{20 August 2013 - 23 August 2013}
{Attended the 
  school
   as partecipant. Website of the school:
   \url{http://presusy2013.ictp.it/}}
\cventry
{Workshop on Ultracold Atoms \& Gauge Theories}
   {International Center for Theoretical Physics (ICTP)}
{Trieste (Italy)}
{13 May 2013 - 17 May 2013}
{Attended 
   the workshop as
   partecipant.
   Webpage of the workshop:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?ida=a12184}}
\cventry
{Workshop on Majorana Fermions, Non-Abelian Statistics and Topological Quantum Information Processing}%
   {International Center for Theoretical Physics (ICTP)}
{Trieste (Italy)}
{20 August 2012 -- 24 August 2012}
{Attended 
   the workshop 
   as
   partecipant. 
   Webpage of the workshop:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?email=0&ida=a11183}}

\cventry
{Lectures of Introduction to Bayesian methods}
{University of Trieste}
{Trieste (Italy)}{}
{February~2010}%
{I attended \emph{as volountear} the Ph.D. course of Introduction to Bayesian methods (Prof.
   E.~Milotti).
   Lectures addresses Ph.D. students in Physics at university of Trieste.
Topics covered include: Bayesian inference, Maximum-Entropy and its applications
to image restoration, EM algorithm, Markov-Chain Monte Carlo, introduction to
naive Bayesian learning and 
Bayesian classifiers (AUTOCLASS). 
Webpage of the course:
\url{http://wwwusers.ts.infn.it/~milotti/Didattica/Bayes/Bayes.html}
}










\end{cventries}
