%  \cventry
%    {Software Engineer \& Security Researcher (Compulsory Military Service)}
%    {R.O.K Cyber Command, MND}
%    {Seoul, S.Korea}
%    {Aug. 2014 - Exp. Apr. 2016}
%    {
%      \begin{cvitems}
%        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
%        \item {Improved functionality on military command and control system for incident response with Java Servlet.}
%        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
%      \end{cvitems}
%    }




\cvsection{Employment}
\begin{cventries}
\cventry
{software development}
{Sainsburys - Digital Lab}
{London, UK}
{February 2016 -- present}
{%
\textbf{Overview:}
   I spent the first couple of months introducing some TDD practises,
   spinning up and maintaining a in-house Jenkins 2.x CI/CD
   OSX server, and writing multi-platform QA-compliant
   E2E acceptance appium Java tests with page object pattern, doing training  and maven templates to encourage the adoption. 
   Since June 2016, I've been leading the android development of the Grocery 
   native app for shopping online. Currently, the app has
    more than 100k unique users.
    \newline
\textbf{Duties and responsibilities:}
\begin{itemize}
\item 
I am developing new features and bug fixing at consistent high velocity, with proven ability to arrange any urgent task and contingency that can arise during the sprint with almost no impact on the sprint requirements
\item 
implementation is challenging because the app uses in-app real-time dynamic scraping
   of the Sainsbury's website plain html as data source
\item Metodology: agile, two-weeks sprints, sprint planning, retro and demo,  releases on the playstore at the end of each sprint
%\item Team: 4 iOS devs, 2 Android devs, QA team, product owner, delivery manager
    \item 
    I have been praised by the company for my hard work
    \item 
    I have been doing mentorship and training of apprentices 
\item 
I'm used to prepare slides to explain benefits and efforts of some implementation choices also to non-technical colleagues
    \item I am assistant coordinator of the functional programming ``guild'', an internal bi-weekly meeting aimed at promoting the adoption of FP within Sainsbury's
\end{itemize}
    \textbf{Preferred technology stack:} Jsoup, Retrofit2 (I have implemented custom converter and calladapter factories to hide the scraping part), Dagger2, basic RxJava2,
    Realm,
   Fresco, firebase, appsflyer. For tests: junit4, mockito, espresso, spoon, appium, wiremock.
   Architectual pattern: clean architecture with mvp on presentation layer. 
\newline
CI/CD: I setup the delivery pipeline on greenhouse CI, configuring lint, unit and espresso tests on aws farm, sonarqube and jacoco.
   \newline The Android app is freely downloadable from Google play store:
   \url{https://play.google.com/store/apps/details?id=com.sainsburys.gol&hl=en}
}
\cventry
{Android software engineer}
{Spotlime}
{Milan, Italy}
{September 2014 -- December 2015 }
{
   \textbf{Overview:}
   Leading the 
   development of the 
   Android native application for 
   Spotlime, a startup aimed  at promoting  the 
   discovery of the best events in Milan, Rome and Florence. 
   \newline
   \textbf{Duties and responsibilities:}
   \begin{itemize}
      \item Development \emph{from scratch} and maintenance of the Spotlime android
	 native application.
      \item Provide level of effort to integrate new functionalities and
	implement. 
      \item 
   Work alongside the marketing team to deliver a user-centric product closer
   to real customer 
   needs, promoting solutions that helps improving UX in response
   to users' feedback and analytics data.
      \item 
   Work alongside server-side and iOS developers to coordinate the upcoming
   releases, following CTO directives.
\item Help to develop Spotlime booking desktop website using mainly server-side JSF and
   primefaces.
\end{itemize}
\textbf{Preferred technologies}: Realm database, Retrofit, Glide, EventBus,
Gson.
   Experience in: REST, client-server data synchronization, offline mode,
   advanced geolocation techniques, Facebook SDK, GCM push notifications
   \newline
   \textbf{More details:}
   %Company website:
   %\url{http://www.spotlimeapp.com/}
   The Android app is freely downloadable from Google play store: 
   \url{https://play.google.com/store/apps/details?id=com.gooutsrl&hl=en}
}

\cventry
{Lead Quality Assurance Analyst} 
{Usablenet - leading global mobile and multi-channel technology company.}
   {Udine, Italy}
{October 2012 -- August 2014}
   {
      After few months working as a quality assurance analyst, I was
      promoted 
   quality assurance team leader at Usablenet, a leading 
  technology platform  company delivering enterprise-level mobile and
  multichannel commerce solutions.
   My responsibilities:
   \begin{itemize}
\item 
  Working in synergy with mobile web
   developers, project manager, solution engineer team and customers to
   consistently deliver high-quality
   products that fulfills customer expectations and end user needs. 
\item Monitor and track project status during all steps, to meet deadlines
   and ensure all scope changes,
 variances and contingences that may arise during the 
 projects lifecycle were visible to all people involved.
 \item 
   Ability to prioritize and track multiple projects in parallel,
    manage  allocation of resources within the team, supervise and support my team
    activities.
 %\item  Be a go-to person.
 \item 
   Proven ability to work under pressure responsibly and fulfilling high
   expectations.
%\item test plan and test cases creation using TestLodge
\item Promote new strategies to speed up effective communication among all
   teams involved in the project, suggesting 
   improvements to current workflows and defining new internal procedures.
\item Debugging and monitoring of %customized web analytics solutions and 
technical requirements (for example requirements involving
   akamai technologies).
\item 247 QA support.
   \item Developing small scripts (mainly using Python+JQL) which help to retrieve project
 information from Atlassian Jira and provide automatic statistical reports about
 project status.
 \end{itemize} 
   Personally responsible as QA analyst of:
   Camelot Group (UK National Lottery, including the
   launch of the mobile website for the new lotto raffle on October 2013), Dell Inc. (22 countries
   including US, UK, China etc), FedEx,
   MaryKay, Selfridges, Surfstitch and many others.
%which requires ability to quickly gain
%familiarity with unknow projects, providing insights which help to spot the root
%cause of the issues and testing if it has
%been solved successfully.
Company website: \url{http://usablenet.com/}}
\cventry
{Teacher (on call)}
{University of Udine}
{Udine}
{2006 -- 2012}
{
   I have been asked to teach  the \emph{Esercitazioni guidate di Fisica per il Corso
      di preparazione al Test di ammissione alla Facolt\`a di Medicina e
      Chirurgia} at the University of Udine (support training lectures
   organized
for candidates to the placement exam for accessing the courses at the faculty
of Medicine).
}
\cventry
{IT technical expert (on call)}
{R.U.E. Risorse Umane Europa (no-profit
   association)}
{Udine}
{September~2011 -- August~2012}
{
   Handling the IT issues in a small office (5 employees): pc, network and
   website maintenance}
\cventry
{\LaTeXe\ typesetter}
{Consorzio per la Fisica}
{Trieste}
{January 2010 -- December 2010}
{   I typeset prof. E.~Gozzi lectures notes for his course of Quantum Mechanics.
   The notes are currently available at 
   \url{http://www-dft.ts.infn.it/~gozzi/QM2.pdf}}
\cventry
{C++ developer as volounteer}
{I.N.F.N. (Istituto Nazionale di Fisica
   Nucleare)}
{Trieste}
{February~2008 -- May~2008}
{Development of a object-oriented C++ library for uniform and non-uniform
   pseudo-random number generations, including some cutting edge algorithms}

\end{cventries}
