
\cvsection{Continuing Education}


\cvsubsection{Coursera}
\begin{cvhonors}
  \cvhonor
{Machine Learning}
{Statement of Accomplishment of Machine Learning course by Professor Andrew Ng
   from Standford University.
   Website of the course:
   \url{https://www.coursera.org/learn/machine-learning/home/info}}
{Coursera}
{2014}

\end{cvhonors}


\cvsubsection{Workshop and schools in Physics}
\begin{cvhonors}
  \cvhonor
{School on Supersymmetry and Unification of Fundamental Interactions (Pre-SUSY 2013)}
{Attended the school as partecipant at International Center for Theoretical
   Physics (ICTP). Website of the school: \url{http://presusy2013.ictp.it/}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{Trieste (Italy)}
%{20 August 2013 - 23 August 2013}
{2013}

  \cvhonor
{Workshop on Ultracold Atoms \& Gauge Theories}
{Attended the workshop as partecipant at International Center for Theoretical
   Physics (ICTP).  Webpage of the workshop:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?ida=a12184}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{Trieste (Italy)}
%{13 May 2013 - 17 May 2013}
{2013}

  \cvhonor
{Workshop on Majorana Fermions, Non-Abelian Statistics and Topological Quantum Information Processing}%
{Attended the workshop as partecipant at International Center for Theoretical
   Physics (ICTP). 
   Webpage of the workshop:
   \url{http://cdsagenda5.ictp.trieste.it/full_display.php?email=0&ida=a11183}}
%{International Center for Theoretical Physics (ICTP), Trieste (Italy)}
{Trieste (Italy)}
%{20 August 2012 -- 24 August 2012}
{2012}

  \cvhonor
{Ph.D. Course of Introduction to Bayesian methods}
{I attended \emph{as volountear} the Ph.D. course of Introduction to Bayesian methods (Prof.
   E.~Milotti).
   Lectures address Ph.D. students in Physics at university of Trieste.
Topics covered include: Bayesian inference, Maximum-Entropy and its applications
to image restoration, EM algorithm, Markov-Chain Monte Carlo, introduction to
naive Bayesian learning and 
Bayesian classifiers (AUTOCLASS). 
Webpage of the course:
\url{http://wwwusers.ts.infn.it/~milotti/Didattica/Bayes/Bayes.html}
}
{Trieste (Italy)}
{2010}%





 \end{cvhonors}









